Sound and Automated Synthesis of Digital Stabilizing Controllers for Continuous Plants

### 2016-10-13 paper/paper.tex
revised contibutions to match experiments

\item We designed and implemented an automatic approach for 
generating {\em corect-by-construction} digital controllers that is 
based on state-of-the-art inductive synthesis techniques.
Our application of program synthesis is non-trivial 
and requires addressing challenges specific to
control systems such as the effects of quantisers 
and FWL. In particular, we found that a two-stage 
verification engine that continuously refines the precision
of the fixed-point representation is key to the performance of our approach 
yielding, in most cases,  a speed-up  
of several orders of magnitude over 
a conventional one-stage verification 
engine.

@@

\subsection{Synthesis for to control}
\label{synthesis-elements}

>>>>

\item We designed and implemented an automatic approach for generating
  {\em corect-by-construction} digital controllers that is based on
  state-of-the-art inductive synthesis techniques.  Our application of
  program synthesis is non-trivial and requires addressing challenges
  specific to control systems such as the effects of quantisers and
  FWL. In particular, we found that a two-stage verification engine
  that continuously refines the precision of the fixed-point
  representation is key to the performance of our approach yielding,
  in most cases, a speed-up of at least two orders of magnitude over a
  conventional one-stage verification engine.

@@

\subsection{Synthesis for control}
\label{synthesis-elements}
